Prag Bat Summary

### 2020-10-28 analysis/summary.Rmd
add cfa reli

library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
#library(psych)
library(readODS)
#library(brms)
library(psy)
library(tidyboot)
library(lubridate)
library(ggpubr)
library(lavaan)
```

@@

```{r}
lavaan_data <- filter(data, round == "R1", test_day == 1) %>%
  group_by(id, task) %>%
  summarise(correct = mean(correct)) %>%
  pivot_wider(names_from = task, values_from = correct)
```

```{r}
model1 <- 'pragmatic  =~ informativeness + novelty + preference + mutual_exclusivity 
          ef =~ card_sorting'

fit <- cfa(model1, data=lavaan_data)
summary(fit)
```

>>>>

library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
#library(psych)
library(readODS)
#library(brms)
library(psy)
library(tidyboot)
library(lubridate)
library(ggpubr)
library(lavaan)
library(blavaan)
library(semPlot)
```

@@

```{r}
lavaan_data_1 <- filter(data, round == "R1") %>%
  group_by(id, task) %>%
  summarise(correct = mean(correct)) %>%
  pivot_wider(names_from = task, values_from = correct)

lavaan_data_2 <- filter(data, round == "R2") %>%
  group_by(id, task) %>%
  summarise(correct = mean(correct)) %>%
  pivot_wider(names_from = task, values_from = correct)

lavaan_data_r1 <- filter(data, round == "R1") %>%
  group_by(test_day,id, task) %>%
  summarise(correct = mean(correct)) %>%
  pivot_wider(names_from = c(task,test_day), values_from = correct)%>%
  na.omit()

lavaan_data_r2 <- filter(data, round == "R2") %>%
  group_by(test_day, id, task) %>%
  summarise(correct = mean(correct)) %>%
  pivot_wider(names_from = c(task,test_day), values_from = correct)%>%
  na.omit()
```
### Reliability

```{r}
model_rel_1 <- '
pragmatic_1  =~ informativeness_1  + mutual_exclusivity_1 + novelty_1 + preference_1
pragmatic_2  =~ informativeness_2  + mutual_exclusivity_2 + novelty_2 + preference_2

pragmatic_1 ~~ pragmatic_2

informativeness_1 ~~ informativeness_2
mutual_exclusivity_1 ~~ mutual_exclusivity_2
novelty_1 ~~ novelty_2
preference_1 ~~ preference_2
'

fit_rel_1 <- cfa(model_rel_1, data=lavaan_data_r1, std.lv = TRUE)

summary(fit_rel_1,  ci = T)

```{r}
model_rel_2 <- '
pragmatic_1  =~ ad_hoc_implicature_1  + mutual_exclusivity_1 + simple_inf_1 + discourse_continuity_1
pragmatic_2  =~ ad_hoc_implicature_2  + mutual_exclusivity_2 + simple_inf_2 + discourse_continuity_2

pragmatic_1 ~~ pragmatic_2

ad_hoc_implicature_1 ~~ ad_hoc_implicature_2
mutual_exclusivity_1 ~~ mutual_exclusivity_2
simple_inf_1 ~~ simple_inf_2
discourse_continuity_1 ~~ discourse_continuity_2

'

fit_rel_2 <- cfa(model_rel_2, data=lavaan_data_r2, std.lv = TRUE)

summary(fit_rel_2, ci = T)

semPaths(fit_rel_2, "std")

fitmeasures(fit_rel_2)

### Relations between constructs

```{r}
model_1 <- '
pragmatic  =~ informativeness  + mutual_exclusivity + novelty + preference
ef  =~ card_sorting
'

fit_1 <- cfa(model_1, data=lavaan_data_1, std.lv = TRUE)

summary(fit_1, ci = T)

semPaths(fit_1, "std")

fitmeasures(fit_1)
```

```{r}
model_2 <- '
pragmatic  =~ ad_hoc_implicature  + mutual_exclusivity + simple_inf + discourse_continuity
ef  =~ card_sorting
'

fit_2 <- cfa(model_2, data=lavaan_data_2, std.lv = TRUE)

summary(fit_2, ci = T)

semPaths(fit_2, "std")

fitmeasures(fit_2)
```

### Bayesian estimation

#### Reliability
```{r}
bfit_rel_1<- bcfa(model_rel_1, 
                   data=lavaan_data_r1, 
                   std.lv = TRUE,
                   n.chains = 4,
                   burnin = 2000,
                   sample = 4000)

summary(bfit_rel_1, ci = T)
```

```{r}

bfit_rel_2 <- bcfa(model_rel_2, 
                   data=lavaan_data_r2, 
                   std.lv = TRUE,
                   n.chains = 4,
                   burnin = 2000,
                   sample = 4000)

summary(bfit_rel_2, ci = T)

semPaths(bfit_rel_2, "std")
```

#### Relations between constructs

```{r}
bfit_1 <- bcfa(model_1, 
                   data=lavaan_data_1, 
                   std.lv = TRUE,
                   n.chains = 4,
                   burnin = 2000,
                   sample = 4000)

summary(bfit_1, ci = T)

```{r}
bfit_2 <- bcfa(model_2, 
                   data=lavaan_data_2, 
                   std.lv = TRUE,
                   n.chains = 4,
                   burnin = 2000,
                   sample = 4000
               )

summary(bfit_2, ci = T)

semPaths(bfit_2, "std")
```
